Results

### 2025-04-10 notebooks/00_index.qmd
update

_unitify(u) = x -> x * u
mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-17")
tmax_wind = DateTime("2021-01-23")

tmin_psp = DateTime("2021-01-16")
tmax_psp = DateTime("2021-01-19")
tmin_wind = DateTime("2021-01-17")
tmax_wind = DateTime("2021-01-18")

@@

tau = Second(30)
psp_events = detect_variance(PSP.B(tmin_psp, tmax_psp), tau)
wind_events = detect_variance(Wind.B(tmin_wind, tmax_wind), tau)
thm_events = detect_variance(THEMIS.B_FGL_GSE(tmin_wind, tmax_wind), tau)
```

>>>>

mva_transform((V, B), tmin, tmax) = mva(V(tmin, tmax), B(tmin, tmax))

```

```{julia}
using SPEDAS: timedim

function tdiff(x; dims=Ti)
    times = SPEDAS.times(x)
    return diff(x; dims) ./ diff(times)
end
```

```{julia}
using Unitful: μ0
using LinearAlgebra: norm

"""
    current_density(B, V)

Calculate the current density time series from the magnetic field (B) and plasma velocity (V) time series.
"""
@views function current_density(B, V)
    _B_in = tview(B, timerange(V))
    dBdt = tdiff(_B_in)

    dBxdt = dBdt[:, 1]
    dBydt = dBdt[:, 2]
    ts = SPEDAS.times(dBdt)
    Vn = tinterp(V[:, 3], ts)
    Jx = @. upreferred(dBydt / (μ0 * Vn))
    Jy = @. upreferred(-dBxdt / (μ0 * Vn))

    B_in = _B_in[1:end-1, :]
    Bx = B_in[:, 1]
    By = B_in[:, 2]
    Bmag = norm.(eachrow(B_in))
    Jpara = @. (Jx * Bx + Jy * By) / Bmag
    Jperp = @. (Jy * Bx - Jx * By) / Bmag
    return (; Jx, Jy, Jpara, Jperp)
end

@b current_density(B, V)
```

```{julia}
tmin_psp = DateTime("2021-01-14")
tmax_psp = DateTime("2021-01-21")
tmin_wind = DateTime("2021-01-15")
tmax_wind = DateTime("2021-01-23")
tmax_wind = DateTime("2021-02-15")

tmin_psp = DateTime("2021-01-16")
tmax_psp = DateTime("2021-01-19")
# tmin_wind = DateTime("2021-01-17")
# tmax_wind = DateTime("2021-01-18")

@@

tau = Second(30)
# psp_events = detect_variance(PSP.B, tmin_psp, tmax_psp, tau)
# wind_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau)
thm_events = detect_variance(Wind.B, tmin_wind, tmax_wind, tau; split=Day(1))
```
